Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-07-24 paper.tex
Minor fix

Two experiments have been conducted for each reproducibility matrix, to evaluate the performance of our 
predictions using (1) ALS without biases, and (2) ALS with biases. 
Results will be evaluated using classification accuracy and compared to (1) a dummy classifier that always 
predicts the value in the majority class and (2) the Random Unreal 
method, used as the baseline sampling technique. All reported values are averages
over 5 repetitions. \todo{Report model parameters, including number of 
factors.} Due to sampling issues, it is possible that the actual 
training ratio obtained with some of the sampling methods does not 
match the target one. We checked that the difference between the target 
and real training ratios was lower than 0.01. We used Spark's ALS model 
as available in package \texttt{pyspark.ml}, with 50 factors, a 
regularization parameter of 0.01, a maximum of 5 iterations and non 
negative constraints set to true.

>>>>

Two experiments have been conducted for each reproducibility matrix, to evaluate the performance of our 
predictions using (1) ALS without biases, and (2) ALS with biases. 
Results will be evaluated using classification accuracy and compared to (1) a dummy classifier that always 
predicts the value in the majority class and (2) the Random Unreal 
method, used as the baseline sampling technique. All reported values are averages
over 5 repetitions. Due to sampling issues, it is possible that the actual 
training ratio obtained with some of the sampling methods does not 
match the target one. We checked that the difference between the target 
and real training ratios was lower than 0.01. We used Spark's ALS model 
as available in package \texttt{pyspark.ml}, with 50 factors, a 
regularization parameter of 0.01, a maximum of 5 iterations and non 
negative constraints set to true.
